Add Plant Functional Type (PFT) labels

### 2021-03-29 R/add_plant_functional_type.Rmd
13 done

@@

  else if(genusSpecies == "Acer circinatum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "vine maple"}

>>>>

unique(cleaned_spectra$scientificName)

@@

  else if(genusSpecies == "Acer circinatum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
                  # or woody shrub? USDA Plants shows both Shrub and Tree growth form
    taxon_pft_lookup$commonName[i] = "vine maple"}

  else if(genusSpecies == "Frangula purshiana"){
    taxon_pft_lookup$pft[i] = "woody_shrub" 
    taxon_pft_lookup$commonName[i] = "Cascara buckthorn"}

  else if(genusSpecies == "Acer rubrum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "red maple"}

  else if(genusSpecies == "Betula alleghaniensis"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "yellow birch"}

  else if(genusSpecies == "Populus tremuloides"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "quaking aspen"}

  else if(genusSpecies == "Tsuga canadensis"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "eastern hemlock"}

  else if(genusSpecies == "Acer pensylvanicum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "striped maple"}
